\vspace{5pt}

{\cventry{2021--Present}{Senior Software Engineer}{Tesla}{Ashok Elluswamy}{}{
\begin{itemize}
    \item[] Work on planning and controls team for Autopilot.
\end{itemize}
}

\vspace{5pt}

{\cventry{2017--2021}{Space Technology Research Fellow}{NASA}{Dr. Julia Badger}{}{
\begin{itemize}
    \item[] Work at NASA JSC for 10+ weeks each year. Integrate research with large (several million lines of code) C++ code base.
    \item[] Apply research in task-motion planning and formal synthesis to Robonaut 2 and Astrobee (See [Kingston ICRA 2020])
\end{itemize}
}

\vspace{5pt}

\cventry{2016--2021}{Graduate Research Assistant}{Rice University}{Dr. Lydia E. Kavraki}{}{
\begin{itemize}
\item[] Apply Machine Learning to task-motion planning to improve scalability (See [Wells RAL 2020])
\item[] Develop finite probabilistic synthesis and applying the same to robot manipulation\\
(See \url{https://github.com/andrewmw94/ltlf_prism} and [Wells EPTCS 2020])
\item[] Mentor graduate student's research in multi-robot planning and control as well as multi-robot task-motion planning (See [Pan IROS 2020])
\item[] Develop tool for stochastic games to model human-robot collaboration
\end{itemize}
}

\vspace{5pt}

\cventry{Summer 2016}{Google Summer of Code}{LLVM/Linux}{Jan-Simon M\"oller}{}{
\begin{itemize}
\item[] Implemented checkers using the Clang static-analyzer for the Linux Kernel\\
(See user andrewmw94 at \url{https://github.com/andrewmw94/llvm_clang_GSoC})
\end{itemize}
}

\vspace{5pt}

\cventry{2013--2016}{Research Assistant}{Catholic University of America}{Dr. Erion Plaku}{}{
\begin{itemize}
\item[] Use discrete leads to motion plan for high-dimensional systems with nonlinear dynamics (See [Wells TAROS 2015])
\end{itemize}
}

\vspace{5pt}

\cventry{Summer 2015}{NSF REU}{DIMACS, Rutgers University}{Dr. Kostas Bekris}{}{
\begin{itemize}
\item[] Extended a proof of probabilistic near-optimality from $PRM^*$ to tree-based planners
\item[] Use shortest paths in different homotopic classes to guide kinodynamic motion planning
\end{itemize}
}
\vspace{5pt}

\cventry{Summer 2014}{Google Summer of Code}{MLPACK}{Dr. Ryan Curtin}{}{
\begin{itemize}
\item[] Implement R-Trees and variants for nearest-neighbor searches\\
(See user andrewmw94 at \url{https://github.com/mlpack/mlpack})
\end{itemize}
}

\vspace{5pt}

\cventry{Summer 2013}{NSF REU}{Florida International University}{Dr. Xin Sun}{}{
\begin{itemize}
\item[] Add a field to a packet header in OpenFlow to make administration of Software Defined Networks more easy and efficient (See [O'Neil HotSDN 2014])
\end{itemize}
}
