\section{Selected Publications}

\vspace{8pt}

\begin{itemize}

\item[]{C. Disselkoen, A. Eline, S. He, K. Headley, M. Hicks, K. Hietala, J. Kastner, A. Mamat, M. McCutchen, N. Rungta, E. Torlak, B. Shaah, and A. M. Wells. ``How We Built Cedar: A Verification-Guided Approach'' in Foundations of Software Engineering (FSE), 2024.}

\vspace{8pt} 

\item[]{J. W. Cutler, C. Disselkoen, A. Eline, S. He, K. Headley, M. Hicks, K. Hietala, E. Ioannidis, J. Kastner, A. Mamat, D. McAdams, M. McCutchen, N. Rungta, E. Torlak, and A. M. Wells. ``Cedar: A New Language for Expressive, Fast, Safe, and Analyzable Authorization'' in Object-Oriented Programming, Systems, Languages, and Applications (OOPSLA), 2024.}

\vspace{8pt} 

\item[]{K. Muvvala, A. M. Wells, M. Lahijanian, L. E. Kavraki, and M. Y. Vardi, ``Stochastic Games for Interactive Manipulation Domains,'' in IEEE Intl. Conf. on Robotics and Automation, 2024. To Appear.}

\vspace{8pt} 

\item[]{S. Bansal, Y. Li, L. M. Tabajara, M. Y. Vardi, and A. M. Wells, ``Model Checking Strategies from Synthesis Over Finite Traces'' in Automated Technology for Verification and Analysis (ATVA) 2023. (\textbf{Best paper award})}

\vspace{8pt} 

\item[]{T. Pan, A. M. Wells, R. Shome and L. E. Kavraki, ``Failure Is an Option: Task and Motion Planning with Failing Executions,'' in IEEE Intl. Conf. on Robotics and Automation, 2022, pp. 1947–1953.}

\vspace{8pt} 

\item[]{S. Bansal, L. E. Kavraki, M. Y. Vardi and A. M. Wells, ``Synthesis from Satisficing and Temporal Goals,'' 36th AAAI Conf. on Artificial Intelligence, 2022.}

\vspace{8pt} 

\item[]{T. Pan, A. M. Wells, R. Shome and L. E. Kavraki, ``A General Task and Motion Planning Framework For Multiple Manipulators,'' IEEE Intl. Conf. on Intelligent Robots and Systems, 2021.}

\vspace{8pt} 

\item[] {A. M. Wells, Z. Kingston, M. Lahijanian, L. E. Kavraki and M. Y. Vardi, ``Probabilstic Synthesis for Robotic Manipulation,'' IEEE Intl. Conf. on Roboticts and Automation, 2021.}

\vspace{8pt} 

\item[]{A. M. Wells, M. Lahijanian, L. E. Kavraki, and M. Y. Vardi, “LTLf Synthesis on Probabilistic Systems,” Electronic Proceedings in Theoretical Computer Science, vol. 326, pp. 166–181, Sep. 2020.}

% \vspace{8pt} 

% \item[]{T. Pan, C. K. Verginis, A. M. Wells, D.V. Dimarogonas and L. E. Kavraki, “Augmenting Control Policies with Motion Planning for Robust and Safe Multi-robot Navigation,” in IEEE Intl. Conf. on Intelligent Robots and Systems, 2020.}

% \vspace{8pt} 

% \item[]{Z. Kingston, A. M. Wells, M. Moll, and L. E. Kavraki, “Informing Multi-Modal Planning with Synergistic Discrete Leads,” in IEEE Intl. Conf. on Robotics and Automation, 2020.}

\vspace{8pt} 

\item[]{He, Keliang, Wells, Andrew M., Kavraki, Lydia E. and Vardi, Moshe. Y.  “Efficient Symbolic Reactive Synthesis for Finite-Horizon Tasks,” in IEEE Intl. Conf. on Robotics and Automation, 2019. (\textbf{Best Paper in Cognitive Robotics})}

\vspace{8pt} 

\item[]{Wells, Andrew M., Dantam, Neil T., Shrivastava, Anshumali and Kavraki, Lydia E.  “Learning Feasibility for Task and Motion Planning in Tabletop Environments,” IEEE Robotics and Automation Letters, 2019. IEEE Robotics and Automation Letters, vol. 4, no. 2, pp. 285–292, Apr. 2019.}

\vspace{8pt} 

\item[]{Wells, Andrew and Plaku, Erion.  “Adaptive Sampling Based Motion Planning for Mobile Robots with Differential Constraints.” Springer LNCS Towards Autonomous Robotic Systems, vol. 9287, pp. 283–295 \url{http://link.springer.com/chapter/10.1007%2F978-3-319-22416-9_32} (\textbf{Best Student Paper Award})}

% \vspace{8pt} 

% \item[]{O’Neil, Michael, Wells, Andrew and Sun, Xin. “Towards a novel and efficient packet identifier design for SDN” HotSDN ‘14 Proceedings of the third workshop on Hot topics in software defined networking, pp. 223-224. \url{http://dl.acm.org/citation.cfm?id=2620728.2620775}}

\end{itemize}