
\small{I am a $5^{th}$ year Ph.D. Student at Rice University advised by Dr. Lydia Kavraki. I will graduate this year. In 2017, I recieved a NASA Space Technology Research Fellowship (now called Space Technology Research Grants (NSTRG)) to conduct research in Task and Motion Planning (TMP) and in Formal Methods (FM) for Robotics. This research includes numerous publications, as well as implementations on physical robots. The research spans an array of topics including (a) applications of Machine Learing to TMP to improve scalability, (b) theoretical work in FM to ensuring or verifying correctness and safety, (c) applications of FM to robotics to enhance robot autonomy while ensuring safety and (d) research in multi-robot planning and control as well as multi-robot task and motion planning. As a NSTRG fellow, my research is relevant to NASA Technology Roadmap 4 (specifically, 4.2.6.1-4.2.6.2, 4.3.2, 4.3.4, 4.4.3-4.4.4, 4.4.7, 4.5.2-4.5.8 and 4.7.2-4.7.5). I have helped individuals at NASA apply my research, collaborating with the Robotics and Intelligence for Human Spacecraft (RIHS) team at the Lyndon B. Johnson Space Center (JSC) and with researchers at NASA Ames. On the hardware side, I have experience on Universal Robotics UR5 robots as well as on NASA's Robonaut 2. I have collaborated with the RIHS team at JSC since 2017 as well as researchers at other labs and universities throughout the world. I have experience leading two small projects of three or four researchers while mentoring a junior Ph.D. student at Rice University, including choosing high-level goals, assigning tasks, and scheduling subgoals to ensure our team meets deadlines.}
